Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-05 edubots_surveys.Rnw
Third paragraph in the introduction section
Updated the third paragraph in the introduction section

In the framework of the EduBots KA2 European project\footnote{https://www.edubots.eu}, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms. A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human. However, in most cases a simple messaging-application attached bot will help the students (and teachers); so neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications (e.g. Telegram, WhatsApp) used nowadays.
% Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
% JJ - feel free to add one 
% Antonio - The thing is I don't catch why are we saying that, since it is supossed that we should 'defend' the use of chatbots (from the project perspective, at least). Or if we don't want to defend them, at least not saying that they are useless most of times. XD
% Moreover, considering that in the following paragraphs we are trying to 'sell' them.
A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{ moor2003turing }, since they are able to answer almost any question fluently, and even pose questions in their conversations. The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}. These automatic systems facilitate the delivery of personalized learning by adapting to students’ pace of learning and providing customized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
adapting individuals' pace of learning, who get customized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

@@

Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 students. The obtained results were analysed with the object of identifying students' actual needs, in \cite{MoraChatbots2021}. The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be with in the class messaging groups, and what do they expect bots and chatbots to do to aid them during their learning process. We concluded that students prefer to use known whatever messaging application, such as Telegram or WhatsApp, they are already using. They also expected chatbots to help them with their scheduling, to provide assignment grades and to search for class material. Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.

% Maybe move it to a different place later
In the present work we aim to complement the aforementioned study with an analysis of teacher attitudes; teachers are the ones that actually would need to use, 
% Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
% JJ - deployment would be done by the university or whoever publishes the system. Deployment and implementation are two different things, anyway
% Antonio - Ok, but what I said is that 'implement' is a synonym of 'program' in this scope, and we write both in the same sentence as different things.
% And deploy does not make sense in this context. I will simply say use - JJ
configure and maybe program chatbots. Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes. We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
\item{ RQ4 - What kind of interaction media features do teachers value the most? }

>>>>

In the framework of the EduBots KA2 European project\footnote{https://www.edubots.eu}, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms. A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human. However, in most cases a simple messaging-application attached bot will help the students (and teachers); so neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications (e.g. Telegram, WhatsApp) used nowadays.
% Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
% JJ - feel free to add one 
% Antonio - The thing is I don't catch why are we saying that, since it is supossed that we should 'defend' the use of chatbots (from the project perspective, at least). Or if we don't want to defend them, at least not saying that they are useless most of times. XD
% Moreover, considering that in the following paragraphs we are trying to 'sell' them.

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
adapting individuals' pace of learning, who get customized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

@@

Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 students. The obtained results were analysed with the object of identifying students' actual needs, in \cite{MoraChatbots2021}. The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be with in the class messaging groups, and what do they expect bots and chatbots to do to aid them during their learning process. We concluded that students prefer to use known whatever messaging application, such as Telegram or WhatsApp, they are already using. They also expected chatbots to help them with their scheduling, to provide assignment grades and to search for class material. Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.
 In this sense, chatbot technology offers a great opportunity for the improvement of tutoring systems \cite{Daniel2016,agarwal2020}, as not all students are comfortable with face-to-face tutoring with the instructor. In fact, in many cases, some students experience stress because of their need to ask a question in front of the entire class. This is why many students refrain to silence in the classroom and tend to contact their teachers later via email. Consequently, this can lead to not only a delay in obtaining answers to their questions but also can cause a significant increase in their teachers’ workload, especially when factoring in the disproportion between the class size and the number of teachers. Hence, the chatbot technology has a potential to mitigate this problem by providing answers to students’ questions and facilitating a dynamic and autonomous learning experience \cite{Griol2014,kim2020}. In addition, using an automated system such as a chatbot, can draw teachers’ attention to topics that students struggle to comprehend or need further assistance in understanding. 
% Maybe move it to a different place later
In the present work we aim to complement the aforementioned study with an analysis of teacher attitudes; teachers are the ones that actually would need to use, 
% Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
% JJ - deployment would be done by the university or whoever publishes the system. Deployment and implementation are two different things, anyway
% Antonio - Ok, but what I said is that 'implement' is a synonym of 'program' in this scope, and we write both in the same sentence as different things.
% And deploy does not make sense in this context. I will simply say use - JJ
configure and maybe program chatbots. Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes. We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
\item{ RQ4 - What kind of interaction media features do teachers value the most? }
